---
title: "Apple Health Data App"
author: "Bruno Ascenso"
date: "November 22, 2018"
output: 
    ioslides_presentation:
        smaller: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
health <- readRDS("myHealth/health.RDS")
```

## Overview

This presentation describes the shiny app created for week 4 assignment of the course Developing Data Products on Coursera.  

The instructions were: "*Write a shiny application with associated supporting documentation*".  

So I decided to (finally) get the data collected by my iPhone and Apple watch and see what's there. For this assignment I downloaded only two metrics:  
- Heart rate (count/min averaged over 1 hour periods)  
- Number of steps per hour

To download the data I used the app QS Access by [Quantified Self Labs](http://quantifiedself.com/).  

The data ranges from **December 19, 2016** (when I started collecting) up to **today**.

## A glance at the data

#### This is how the data looks like:
```{r}
str(health)
head(health)
```


## Usage of the app

The app is available at: https://bascenso.shinyapps.io/myHealth/  

It plots two metrics:

### 1. Histogram of heart rate
Select a date range and it will show a histogram plot of my heart rate between those two dates, along with min, max and mean statistics.

### 2. Plot of steps
Select a date range and a grouping period and it will show a plot of the steps that I walked between those dates (grouped by day, week or month).


## Sample output
This is how the output looks like:

```{r, fig.width=8, fig.height=2.3}

stepsData <- health[(as.Date(health$finish) > as.Date("2017-12-01")) 
                    & (as.Date(health$finish) < as.Date("2018-10-31")), c("finish", "steps")]

stepsData$period <- strftime(stepsData$finish, format = "%Y-%b")

p1 <- ggplot(health[(health$hrate != 0) , ])
p1 <- p1 + aes(hrate)
p1 <- p1 + geom_histogram(binwidth = 5, color = "red", fill = "orange")
p1 <- p1 + theme_classic() + theme(legend.position = "none")
p1 <- p1 + labs(x = "Heart rate (count/min)", y = "Number of occurrences")
print(p1)

p2 <- ggplot(stepsData)
p2 <- p2 + aes(period, steps, fill = steps)
p2 <- p2 + geom_bar(stat = "identity", fill = "skyblue")
p2 <- p2 + theme_classic() + theme(legend.position = "none")
p2 <- p2 + labs(x = "Month", y = "Total steps")
print(p2)

```

